\section{24.11.02}

I have done it, I don't really know what I have done differently, but it works.
There is still the issue with Msg not being registered correctly, but I think
that's an easy fix.

We had a Magnolia Workshop this week, learned \textit{some} stuff, like, the
IDE and Compiler should communicate using LSP, (insane!). But more interesting
stuff, I have a lot of UX I need to consider, my supervisors expect IDE
functionality, and I should make a wishlist of Plugins to develop.

\begin{itemize}
  \item Plugin Debugger
  \begin{itemize}
    \item Display State
    \item Display Msg's being sent
    \item Check if there are state collisions
    \item Check if there are Msg collisions
  \end{itemize}
  \item Dependency Viewer
  \begin{itemize}
    \item Showcase JS
  \end{itemize}
  \item File Explorer
  \item Text Editor
  \begin{itemize}
    \item Use existing JS
  \end{itemize}
  \item Rendering Framework
  \begin{itemize}
    \item Facilitate ease of pre-DOM-manipulation
  \end{itemize}
  \item Mini-LSP-Client
  \begin{itemize}
    \item Hover functionality
    \item GOTO Declaration
  \end{itemize}
\end{itemize}

In state changes, plugins should only return \textit{what} they change, not the
entire state. I think this will be a good change, since not only will it ensure
that overrides are easier to detect, (since we can compare states), states from
plugins are smaller, and there will be less unnecessary duplications.

Again, unit tests should've been made ages ago, my state coalescing in the
frontend should've had unit tests. I'll make some next time.


\section{24.11.03}

What is a good way to correct state collisions? Just not allow it? Error on
collisions? Feels like it should happen at compile-time, and not runtime, but I
can't check until runtime. Maybe I should filter out plugins with collisions,
and not call them, just log it. Could be an idea. I guess that's what should be
done, since this collision only happens once, since the new architecture is to
only return the changed field, instead of the entire state. I could probably do
something like this:

// Get the state change along with the plugin name
const new_state =
  window.plugins.key_values.map(a ⇒ (fst(a), snd(b).update(msg, old_state)));
// Get duplicates
const collisions = Array.duplicates(TMap.Eq)(new_state);
// Print them
if (collisions.length !== 0) console.error("Collisions: ", collisions);
// Get unique plugins, based on plugin name
// similar to: map head \$ map group \$ map (update msg old_state) plugins, I think
setModel(A.unique(TMap.Eq)(new_state));


\section{24.11.06}

I've started work on unit tests for the frontend. I can \textit{easily} create
tests for the frontend, since all backend calls can be mocked, and I can supply
my own pseudo-react-state, which my different functions manipulate, to ensure
correctness. The plan for this month will to be finish the wanted
functionality for v1.0.0, two months late. I just need to figure out some good
tests.

I've spent like 5 hours, (with breaks), writing tests just for my utility
functions. This is going to take weeks.


\section{24.11.07}

Discovered something interesting. I can basically mock the entirety of the
frontend. So, testing JSPS can be really extensive, ensuring the logic holds.
I am knee-deep in \dots I don't know, Functional Programming? Logic?
Category Theory? Creating equalities, monoids and such for my types, so that I
can use the fp-ts library fully. I have the Haskell implementation of groupBy
open so that I have a starting of point for it in my own code.

I got to the point of writing tests for state-updating, and then I figured I
should rewrite my update function, to add logging for state-collisions. Similar
to what I discussed the other day. I think it'll work great.


\section{24.11.08}

Plugins should be a list of Plugin Name, and the Plugin, so that one, (me), can
narrow down which Plugin causes what problem.

It is super boring to write tests. This is killing me. Wrote a fun function
for state change, which made me feel smart, but I also forgot the name of
\texit{unzip}, which made me feel stupid. I was talking to some other students,
and they pointed out something I should probably mention. I am writing
functional TypeScript. Which is not a thing, in the sense it is not optimized.
So my code might be really slow. Hopefully this is not the case. Either way,
this is something I can see easily with E2E-testing, which I only have for the
frontend, not the backend. I think I'll aim for writing these test's til the end
of this month, and then start on creating the dependency plugin, in TypeScript.
Hopefully I've found a smart solution for compiling TypeScript into JavaScript.
And it will be a good test of the plugin system.

I think I am going to say I am done with unit tests for today. I also did some
logic-changes, (which I discovered when creating the tests), so I want to see
if I can get the counter example to work. Then maybe I'll look into some
JSP-Util library.

Took one minute. I think I am starting to get a good system/architecture.

It is pretty simple to create a JSP-Util Library, the only issue is that LSP
help can be tricky to do. But that is a future problem, if it even is a
problem.
<<<<<<< HEAD


\section{24.11.09}

I think I can release v1.0.0, just need to write some documentation, and then
I'll build some files, and finish.

I can build for Windows and Linux, but building for macOS means I have to get
my hands on a macOS machine or a WM, or get my CI/CD to work again.

Tried to do CI/CD stuff, but GitLab-runner issue is a recurring problem. The
ones I tried to create have not been online for two months, (about the time
since I did CI/CD work), and the universities' is also offline! I hope it comes
online tomorrow, and that I remember to turn on my runner.


\section{24.11.10}

Back on the CI/CD-grind, this sucks. After I migrated to Tauri-2.0, and
migrated to ViteJS, my Tauri-Image is missing dependencies, and it's the same
process as before, building the image, (which takes 11 minutes, I should've
fixed this a long time ago), and then re-running the pipeline. Just to find out
I am missing another library. I feel Cargo should know what dependencies crates
have, but this is only discovered during compile-time.

It takes around 16 minutes to build now, I hate doing CI/CD. But I am close to
getting a NSIS build working, i.e. Windows build to work without it being
Windows.


\section{24.11.09}

I think I can release v1.0.0, just need to write some documentation, and then
I'll build some files, and finish.

I can build for Windows and Linux, but building for macOS means I have to get
my hands on a macOS machine or a WM, or get my CI/CD to work again.

Tried to do CI/CD stuff, but GitLab-runner issue is a recurring problem. The
ones I tried to create have not been online for two months, (about the time
since I did CI/CD work), and the universities' is also offline! I hope it comes
online tomorrow, and that I remember to turn on my runner.


\section{24.11.14}

Started utilizing the issue system in GitLab, my thought process is that this
will make it easier to both keep track on what I am working on, and make it
easier to switch between tasks, because some of them are less interesting.


\section{24.11.15}

The only problem with doing this issue-system, is that taking notes is a little
bit harder.

I have made plugin installation the way I wanted, as script-tags, and made a
demonstration of how to use this system alongside an external JavaScript
library. But I've done some thinking, do I need to use React? I don't think so.
But, it does give a lot of handy things for free. Like optimized rendering,
\textit{easy} update handling.
I think I should at least analyze it, and write a few paragraphs about my tech
stack choice, among them being React.

Maybe Haskell?


\section{24.11.16}

I think it would be possible to do what Tauri does, but in Haskell, with
something like threepeny-gui https://heinrichapfelmus.github.io/threepenny-gui/
and electron https://www.electronjs.org/. This would be cool, but I think I
should focus on creating the first few plugins, and maybe look at re-writing
everything to Haskell. I think it would be a fun experience.

But, to the real matter at hand. My current Plugin setup, should work
regardless of what tech stack I have. I have a trivial-JSP, that renders the
dependency graph using the D3 JS-library. It does this by exposing an extra
function, that another JSP is calling, when it receives a Msg.

All I need now, are two Plugins, one that acts as a file explorer, and another
that can parse the dependencies between the files. Maybe a mini-LSP?

Something has happened, so Rust plugins don't work anymore. I don't know what,
but I realized something, I would like to debug Rust Plugins, like I debug
JSP's, being able to interact with them. There are a few ways I can achieve
this. I could add this functionality to the CLI tool I want to make, or I
could change the way I do backend plugins, install them the same way I install
JSP. This would just be an invoke-call.


\section{24.11.17}

I am going to redesign the standard library to fix memory leaks.

I think I should refactor the Tauri app to just Purescript, I think just
utilizing the "purity" of plugins should be enough when re-rendering.
Furthermore, I hope I can find something that does the V-DOM stuff for me. If
just the window object is used, it would be easy to just inject functions
wherever, like the state validation logic. Or rendering. We'll see, for now I'll
just "half-ass" this dependency viewer plugin.

I think the dependency viewer thing works, but Magnolia is so large, it takes a
long time to parse it into a tree. I need to create some efficient way to
navigate it.


\section{24.11.22}

Done some plugin work, the dependency viewer works, it was not Magnolia, but
skill-issue that was the issue. I tried to read the entire .svn folder, which
I assume is a large one. Did some change on how I do stuff as well, instead of
doing stupid splitting of the file, I changed it to regex. The graph looks
ugly, but it works. If I want to make it prettier, I need to be better at D3,
the JavaScript visualization library I am using. Which I cannot be bothered to
do. Instead, I will create the debug-plugin, which should let me enable and
disable plugins. I kinda want to do this in PureScript, but it is frustrating 
to work with, since Array and lists are two different things, and I would
rather be working with Haskell, but I cannot be bothered with learning to
compile it to JavaScript.

The more I am working with PureScript, the more annoyed I am becoming. Why are
same concepts in PureScript not translated as the same concept in JavaScript?
It not being a one-to-one mapping on basic stuff like tuples is very annoying.

The encoding/decoding is so close, and to \textit{fix} it I have to write so
much shitty code.
