\section{25.03.10}

I've been doing very little coding, even though the \textit{due} date for the
refactor is coming. (I've put it to the end of March). I think I am a little
frozen, with the amount of work I have. Although, I don't think it's that much
work, I just want to do other stuff. When I get the feedback for my first draft,
I will probably drop coding to fix that. Anyway, my general plan is this:

\begin{itemize}
  \item Modules are now a compile-time-inclusion
  \item Do the project in Haskell
  \item Figure out a way to do the new architecture
\end{itemize}

I think if the last point fails, I can still use what I learned in the failure,
to implement a shitty version in TypeScript, in the existing project. Because
no matter what I do, I need threads. This can be done in JavaScript, with
\textit{Web Workers}, but I would prefer to do it in Haskell, because that's the
language I \textit{think} in. (Not to brag or anything, but I think). My idea
about the thread stuff is that for each part of the Core, a thread runs,
managing that part. So one thread for the state, ui and event handlers.

I think these can exist independently, so using some library or something for
threading, to aid this, would be smart. Because any update in the thread is due
to an event, I could develop, say, the state thread first, and test it by
sending in some state modifications, which it immediately updates the state
with. Unsure if it should be per modification, or per event, atm.


\section{25.03.12}

I think the dual state/ui management is unnecessary. The reason I had it like
that, was due to the necessity of being able to convert between the State
representation in the Core, and to JSON for the modules, but now that I've moved
away from JSON communication between modules, I don't need that mapping, and can
therefore change how is the State is represented, like by removing Object, and
just having [(String, Value)], where if someone has an object, it is still field
and value, but with a separator, like normal JavaScript Object indexing.


\section{25.03.13}

Integrate the Event Handler into the Module?

\section{25.03.14}

Had a presentation yesterday, at BLDL, went okay, got some good questions which
I should've written down, but now I've forgotten the specifics. They were
something along the lines of:

\begin{itemize}
  \item How does modules communicate?
  \item Does keeping a module \textit{pure} increase the complexity for a module
    developer?
  \item What has been done by keeping bad-actors from executing scripts?
\end{itemize}


\section{25.03.19}

Code is not working, and I am not sure if I'll ever get it too work. If not,
I'll be going back to Rust, make some shitty code, and write for the rest of the
time I am at UIB.
