\chapter{Optimizing instructions sets} \label{app:a}

The following appendix discusses how we can optimize an instruction set. When we
use the term \textit{optimize}, we mean to reduce the amount of instructions.
This can be achieved in a few different steps. \textbf{Instruction} is a
recursive data type, parameterized by \textbf{T}. Since an \textbf{Instruction}
form a monoid\footnote{See section \ref{sec:moD3} in chapter \ref{cha:impl}}
structure, we can apply some of the theory from algebraic structures on our
\textbf{Instruction} variant, optimizing it. The goal of this optimization, is
to see if an \textbf{Instruction} tree contains any no-operations, and prune it.


\section{Pruning the instruction tree}

An \textit{unnecessary} operation is one that leads to an \textbf{NoOp}, which
is the case of inversable \textbf{Instruction}s. This inversability does not
occur on all \textbf{Instruction}, hence it forming a monoid and not a group,
but there are cases where we have inverses, meaning we get \textbf{NoOp}s. If we
do a remove instruction, and then an add, the remove instruction is an
\textbf{NoOp}. If, however, we do the opposite, first add, then remove, we get
an \textbf{NoOp} for both instructions.

Furthermore, since we have the idempotency property on add and remove,
regardless of how many times we repeat the same instruction, it is the same as
doing it just once, meaning we can reduce a series of the same instructions into
a series of no-operations, and a singular instruction.

This gives us four rules which we can apply to our instruction tree:

\begin{equation} \label{eq:apx1}
  Rem_T \odot Add_T \implies NoOp \odot Add_T \implies Add_T
\end{equation}

\begin{equation} \label{eq:apx2}
  Add_T \odot Rem_T \implies NoOp
\end{equation}

\begin{equation} \label{eq:apx3}
  Add_T^1 \odot Add_T^2 \odot \dots \odot Add_T^N \implies Add_T^1 \odot NoOp^1 \odot \dots \odot NoOp^{N - 1} \implies Add_T^1
\end{equation}


\begin{equation} \label{eq:apx4}
  Rem_T^1 \odot Rem_T^2 \odot \dots \odot Rem_T^N \implies Rem_T^1 \odot NoOp^1 \odot \dots \odot NoOp^{N - 1} \implies Rem_T^1
\end{equation}

The optimalization function is not parameterized by a strict variant of
\textbf{T}, meaning it works the same regardless of \textbf{T}. In the
\gls*{ide} the \textbf{Instruction}s are parameterized by \textbf{Value},
\textbf{Html}, \textbf{Attr} and \textbf{String}. The last three are specific to
\gls*{ui} modification, and the last two are modifications on specific
\textbf{Html} instances. This means that if an \textbf{Instruction}
parameterized by \textbf{Html}, is of the \textbf{Rem} variant, we know all
other \gls*{ui} \textbf{Instruction}s pertaining to the removed \textbf{Html}
variant are \textbf{NoOp}s.

\begin{code}[H]
  \lstinputlisting
   [ language=Rust
   , caption={Instruction (Rust)}
   , label=lst:aInst
   , firstline=4
   , lastline=16
   ]{./libs/rust/core-std-lib/src/instruction/inst.rs}
\end{code}

In Rust we can have generic data types, as shown in listing \ref{lst:aInst}, by
the type parameter, $T$, but we have to restrict the type $T$ to a type that
implements the trait \textbf{PartialEq}, which means we can use equality on it.
We need this restrictions, because the attribute macro \textbf{Instruction} has.
These macros generate the needed code to implement the different traits:

\begin{itemize}
  \item Debug: Enables the implementer to be printed to \textit{stdout}
  \item Default: Implements a default variant of the implementer type, in this
    case, NoOp
  \item Clone: Implements a simple \textbf{clone} method, to create an owned
    instance of a borrowed value
  \item Deserialize \& Serialize: Implements the needed methods for encoding
    and decoding a variant to a \gls{json} representation
  \item TS: Enables automatic TypeScript type generation of the variant
\end{itemize}


\section{Implementation}

We first start the optimalization step, by removing all NoOps, and then
flattening the instructions, by using the \textbf{opt} and \textbf{flatten}
methods, shown in listings \ref{lst:opt} and \ref{lst:flatten} respectively.

\begin{code}[H]
  \lstinputlisting
   [ language=Rust
   , caption={
     Opt method (Rust): Uses a match statement and a guard to match on a
     \textit{slice}, (reference to a Vec). The guard lets us add a predicate to
     our branch, in this case, if y \textit{matches} an NoOp. If it is an empty
     slice, it's a NoOp, otherwise, it will be an Instruction with all NoOps
     recursively removed.
   }
   , label=lst:opt
   , firstline=119
   , lastline=151
   ]{./libs/rust/core-std-lib/src/instruction/opt.rs}
\end{code}

\begin{code}[H]
  \lstinputlisting
   [ language=Rust
   , caption={
     Flatten method (Rust): Note the lack of return statements, this is because
     the last expression in a function in Rust, is returned, if the expression
     does not end with a semicolon.
   }
   , label=lst:flatten
   , firstline=17
   , lastline=26
   ]{./libs/rust/core-std-lib/src/instruction/opt.rs}
\end{code}

In listing \ref{lst:count}, we then iterate over each instruction in the
sequence, and mapping each field and value to a counter. If it's an Add
instruction, the counter is incremented, if it's a Rem instruction, the counter
is decremented. We don't have a way to inform the compiler that we have removed
all NoOp and Then instructions, and we need complete match-statements, so we add
a catch-all with an \textit{unreachable} macro, which will \textit{panic} with
the supplied message. This is commonly used to represent a state that is
unreachable, but something the compiler can't prove.

\begin{code}[H]
  \lstinputlisting
   [ language=Rust
   , caption={Modification counting (Rust)}
   , label=lst:count
   , firstline=50
   , lastline=79
   ]{./libs/rust/core-std-lib/src/instruction/opt.rs}
\end{code}

Finally, in the listing \ref{lst:fold}, we \textit{unflatten} the sequence of
instructions, and check the count for each Add and Rem Instruction. If it is
above $0$, then that means we have added that field-value pair more times than
removing it, but we can still only add it once, so we set the count to $0$, and
return a Then instruction, since we have the accumulated instructions along with
the current Add instruction. If the count is less than $0$, then it means we are
removing it more times than adding it, similarly, we can only remove it once, so
we set the count to $0$, and combine the accumulated instruction, with the Rem
instruction. Because of our \textbf{combine} implementation, we can be sure that
the initial NoOp element is removed as soon as possible.

\begin{code}[H]
  \lstinputlisting
   [ language=Rust
   , caption={Instruction folding (Rust)}
   , label=lst:fold
   , firstline=81
   , lastline=112
   ]{./libs/rust/core-std-lib/src/instruction/opt.rs}
\end{code}
