\documentclass[UKenglish]{beamer}

\usepackage[T1]{fontenc}

\usepackage{graphicx}

\usepackage[normalem]{ulem}

\usepackage{newclude}

% Haskell
\usepackage[cache=false]{minted}

\usepackage{tikz}
% Overlay effec
\usetikzlibrary{shapes.geometric,positioning,shapes.symbols,overlay-beamer-styles}

%% UIB
\usepackage[utf8]{inputenx} % For æ, ø, å
\usepackage{csquotes}       % Quotation marks
\usepackage{microtype}      % Improved typography
\usepackage{amssymb}        % Mathematical symbols
\usepackage{mathtools}      % Mathematical symbols
\usepackage[absolute, overlay]{textpos} % Arbitrary placement
\setlength{\TPHorizModule}{\paperwidth} % Textpos units
\setlength{\TPVertModule}{\paperheight} % Textpos units
%%

\title{What is an IDE?}
\author{Nils Michael Fitjar}
\date{\today}

\begin{document}

\frame{\titlepage}

\section{Project}
\begin{frame}{Project}
  Create a modular IDE.
  (modular in this context, meaning it can be extended with plugins)
\end{frame}

\section{Showcase}
\begin{frame}{IDE}
  So, here is my IDE:
\end{frame}

\begin{frame}{IDE Features}
  \begin{itemize}
    \item Dynamically loading of Plugins
  \end{itemize}
\end{frame}

\section{Plugins}
\begin{frame}{Loading of Plugins}
  A Plugin, is a shared-object-file, that is dynamically loaded
  during startup.
  It needs to expose, an init, view and update function.
\end{frame}

\begin{frame}{Plugin Example}
  \include{../../code/plugin-architecture}
\end{frame}

\begin{frame}{What is an IDE?}
  \begin{enumerate}
    \item Before Woke: Text editor and a compiler.
    \item After Woke: Text editor, Debugger, File Explorer,
    Syntax Highlighting, LSP, Compiler/Interpreter, Linter, Integrated-VCS,
    Themes, Integrated-Terminal, Workspace, Language Agnostic, Easy Setup, AI
    and more
  \end{enumerate}
\end{frame}

\begin{frame}{What is a Text Editor?}
  \begin{itemize}
    \item A file is just a string of bytes
    \item Need some form of abstraction on this to achieve a standard text
    editor movement
    \item You can group them by newlines
    \item But your syntax highlighter might want a different representation of the text
    \begin{itemize}
      \item Like grouping multi-line-comments
      \item \include{../../code/comment-example}
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Example Text Editor Parts*}
  \center
  \include{../../figures/text-editor}
\end{frame}

\begin{frame}{Example Text Movement}
  \begin{itemize}
    \item Can move by individual symbols, words, lines, pages
    \begin{enumerate}
      \item Group by individual symbols
      \item Group symbols by word
      \item Group words by line
      \item Group line by page
    \end{enumerate}
    \item Can jump to symbol at start/end of word, line, page
  \end{itemize}
\end{frame}

\begin{frame}{What's missing?}
  \begin{itemize}
    \item For the text editor: editing of text
    \begin{itemize}
      \item Saving
      \item Opening
      \item Closing
      \item Deleting
    \end{itemize}
  \end{itemize}
\end{frame}

\end{document}
