\section{Task}
\SectionPage

\begin{frame}
  \frametitle{Task}
  \begin{itemize}
    \item Develop a new, \textit{modular}, IDE for Magnolia
    \begin{itemize}
      \item What is Magnolia?
      \item What is an IDE?
      \item Why create a \textit{new} IDE?
      \item Why modular?
    \end{itemize}
  \end{itemize}
\end{frame}

\section{What is Magnolia?}
\SectionPage

\begin{frame}
  \frametitle{Magnolia}
  \begin{itemize}
    \item A research programming language being developed by
      Bergen Language Design Laboratory at the University of Bergen
    \item Uses something called \textit{concepts}
    \item Similar to an Java interface.
    \item A concept declares
    \begin{itemize}
      \item Types
      \item Operations on those Types
      \item Axioms that specify the behavior of the Operations
    \end{itemize}
    \item A concept can use other concepts, and rename the Types and Operations
      in the concept, this is called renaming
    % TODO: Source?
    \item It is useful for a Magnolia Developer to be able to see the different
      renamings of a concept
  \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Simple Semigroup example}
    TODO: Add this
\end{frame}

\section{What is an IDE?}
\SectionPage

\begin{frame}
  \frametitle{The Solution To The Problem}
  \begin{quote}
    "It works on my machine." \textemdash Intern
  \end{quote}
  \begin{itemize}
    % TODO: Insert The Good, The Bad, and The Ugly picture, maybe?
    \item The Terminal, The Text Editor and The Compiler
    \pause
    \item Missing/incomplete:
    \begin{itemize}
      \item Libraries
      \item Environment variables
      \item Configurations
      \item Scripts
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Integrated Development Environment}
  \begin{itemize}
    \item Easier to onboard new developers
    \item Other quality of life improvements
    \begin{itemize}
      \item File explorer
      \item Project manager
      \item Version Control System integration
      \item Syntax Highlighting
      \item Integrated debugging
      \item \dots
    \end{itemize}
  \end{itemize}
\end{frame}

\section{Why create a \textit{new} IDE?}
\SectionPage

\begin{frame}
    \frametitle{If It Ain't Broke}
    % TODO: Could probably expand this
    The current Magnolia IDE
    \begin{itemize}
        \item Made using an old version of Eclipse
        \item Uses deprecrated Eclupse plugins
        \item Installation process is complex
        \item In INF220, two weeks is set aside for students to install it
        \item Integrated with the Magnolia Compiler
    \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Forking VSCode And Adding AI}
  \begin{itemize}
    \item Current IDEs cannot have good support for experimental programming
      languages
    \item VSCode or similar IDEs could deprecrate needed functionality
    \item The installation process would then be complex
    \item Deep understanding of the used IDE is needed
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Why Modular?}
  \begin{itemize}
    \item Magnolia is still in development
    \item The Magnolia toolchain is being developed in parallel
    \item Nothing to create an integrated development environment with, yet.
    \item Modularity allows for future discoveries to be quickly adopted into
      the IDE
    \item Lowers the onboarding time for future maintainers
    % TODO: Add more
  \end{itemize}
\end{frame}
