\documentclass[runningheads]{llncs}

\input{settings}

\title{Modular IDE}

\author{Nils Michael Fitjar\inst{1,2}}

\authorrunning{Nils Michael Fitjar}

\institute{Western Norway University of Applied Sciences\\
\email{798183@stud.hvl.no}
\and
University of Bergen\\
\email{nfi005@uib.no}
}

\begin{document}

\frontmatter

\maketitle

\chapter{Abstract} \label{abstract}

\begin{abstract}
  This paper introduces a Modular, \textit{Zero Core}, Application, to serve as
  an Integrated Development Environment (IDE) for experimental programming
  languages, addressing limitations in traditional IDEs. While standard IDEs are
  crucial in software development, their support for experimental languages is
  often inadequate. This can and, has been solved by extensively using the
  plugin/module architecture of existing IDEs. However, relying on
  \textit{niche} plugins/functionality is not future safe.
  % TODO: Rewrite this sentence
  This project proposes a modular IDE to extend its lifespan and enhance support
  for experimental languages. Analyzing the essential features of traditional
  IDEs and the need for adaptability to new paradigms and tools. Magnolia, a
  research programming language developed at UIB, serves as a case study,
  highlighting its unique characteristics and the necessity for a specialized
  IDE. The primary research question explores how modularization facilitates the
  design and implementation of experimental programming languages. Specific
  modules tailored for experimental languages, including Abstract Semantic
  Representation (ASR) Transformation, Term Algebras, MoA translation, and
  Syntactic Theory Functor (STF), are outlined. To showcase the usefulness of
  a modular approach, the modules needed to extend the core application to an
  IDE will be implemented.
  \keywords{Modularization \and IDE \and Magnolia.}
\end{abstract}

\tableofcontents

\mainmatter

\chapter{Introduction} \label{ch:intro}
\input{sections/000_introduction}

\chapter{Background} \label{ch:background}
\input{sections/001_background}

\input{sections/002_research_question}

\chapter{Modules} \label{ch:module}
\input{sections/003_modules}

\input{sections/004_implementation}

\input{sections/005_architecture}

\input{figures/integration-tests}

\printbibliography

\end{document}
